Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-23 outputs/paper/paper.qmd
fixed table styling

knitr::kable(sample_bus_delay, col.names = c("Date", "Line", "Time", "Day", "Location", "Cause of Delay", "Min Delayed", "Min Gap", "Direction", "Vehicle"), align = c("l","c", "c", "c", "c","c", "c", "c", "c","c"))
```

@@

knitr::kable(sample_streetcar_delay, col.names = c("Date", "Line", "Time", "Day", "Location", "Cause of Delay", "Min Delayed", "Min Gap", "Bound", "Vehicle"), align = c("l","c", "c", "c", "c","c", "c", "c", "c","c"))
```

@@

knitr::kable(sample_subway_delay, col.names = c("Date", "Time", "Day", "Location", "Delay Code", "Min Delayed", "Min Gap", "Bound", "Line", "Vehicle"), align = c("l","c", "c", "c", "c","c", "c", "c", "c","c"))
```

>>>>

knitr::kable(sample_bus_delay, col.names = c("Date", "Line", "Time", "Day", "Station", "Cause of Delay", "Min Delay", "Min Gap", "Direction", "Vehicle"), align = c("l","c", "c", "c", "c","c", "c", "c", "c","c"))
```

@@

library(knitr)
library(kableExtra)

# Generate the table with automatic text wrapping for column names
knitr::kable(sample_streetcar_delay, 
             col.names = c("Date", "Line", "Time", "Day", "Station", "Cause of Delay", "Min Delay", "Min Gap", "Bound", "Vehicle"), align = c("l","c", "c", "c", "c", "c", "c", "c", "c", "c")) 
```

@@

knitr::kable(sample_subway_delay, col.names = c("Date", "Time", "Day", "Station", "Delay Code", "Min Delayed", "Min Gap", "Bound", "Line", "Vehicle"), align = c("l","c", "c", "c", "c","c", "c", "c", "c","c"))
```
